### 2016-07-06 ansi-isolation.tex
Reverted changes to ansi-isolation.
Edits.

We now describe specifications of standard isolation guarantees
expressed as constraints over trace well-formedness. For brevity and
convenience, we adopt few notations in this and subsequent sections.
An execution trace is destructed as ($\A$,$\visZ$) whenever individual
components of the pair are needed. Otherwise, it is written as $\E$.
Sometimes, the dot notation (\eg~$\E.\A$) is also used. Since $\A$ and
$\visZ$ are both sets, we lift the operations on sets to pairs of sets
when updating $\E$. For example, $\E' = \E \cup
(\{\eta_2\},\{(\eta_1,\eta_2)\})$ expands to $\E' = (\E.\A \cup
\{\eta_2\},\,\E.\visZ \cup \{(\eta_1,\eta_2)\})$.  When $\psi$ is a
formula, $\underE{\psi}$ denotes the interpretation of $\psi$ in the
context of the trace $\E$. Such interpretations are defined on a
case-by-case basis in Figs.~\ref{fig:rel-defs}
and~\ref{fig:ansi-isolation}.

@@

Fig.~\ref{fig:ansi-isolation} shows various isolation guarantees
defined as propositions indexed by transaction identifiers.
Transaction $T_j$ is said to have experienced \emph{read-my-writes}
visibility under $\E$ if every effect ($\eta_1$) of $T_j$ is visible
to every subsequent effect ($\eta_2$) of the same transaction in $\E$.
This lets $T_j$ to never lose its own updates. Monotonic visibility
adds one more constraint to \emph{read-my-writes}; besides requiring $\eta_1$
to be visible to $\eta_2$, it also requires every effect ($\eta$)
visible to $\eta_1$ in $\E$ to be visible to $\eta_2$ as well. Thus,
later operations in a transaction witness at least the same set of
effects witnessed by the earlier operations, if not more (hence,
``monotonic'' visibility). Atomic visibility allows an effect
$\eta_2$ of $T_j$ to witness an effect $\eta_1$ of $T_i$ only if all
effects of $T_i$ in $\E$ are also visible to $\eta_2$. Atomic
visibility thus prevents a transaction from being partially visible.
However, atomic visibility does not prevent an uncommitted transaction
from being visible. This is addressed by \C{CommitVis}, which requires
the commit effect of $T_i$ to be visible whenever any effect of $T_i$
is visible.

>>>>

We now describe specifications of standard isolation guarantees
expressed as constraints over trace well-formedness. For brevity and
convenience, we introduce some notations that are used in the following
sections.  An execution trace is destructed as ($\A$,$\visZ$) whenever
individual components of the pair are needed. Otherwise, it is written
as $\E$.  Sometimes, the dot notation (\eg~$\E.\A$) is also
used. Since $\A$ and $\visZ$ are both sets, we lift the operations on
sets to pairs of sets when updating $\E$. For example, $\E' = \E \cup
(\{\eta_2\},\{(\eta_1,\eta_2)\})$ expands to $\E' = (\E.\A \cup
\{\eta_2\},\,\E.\visZ \cup \{(\eta_1,\eta_2)\})$.  When $\psi$ is a
formula, $\underE{\psi}$ denotes the interpretation of $\psi$ in the
context of the trace $\E$. Such interpretations are defined on a
case-by-case basis in Figs.~\ref{fig:rel-defs}
and~\ref{fig:ansi-isolation}.

@@

Fig.~\ref{fig:ansi-isolation} shows various isolation guarantees
defined as propositions indexed by transaction identifiers.
Transaction $T_j$ is said to have experienced \emph{read-my-writes}
visibility (\C{RMWVis}) under $\E$ if every effect ($\eta_1$) of $T_j$
is visible to every subsequent effect ($\eta_2$) of the same
transaction in $\E$.  This lets $T_j$ to never lose its own updates.
Monotonic visibility (\C{MonotonicVis}) adds one more constraint to
\emph{read-my-writes}; besides requiring $\eta_1$ to be visible to
$\eta_2$, it also requires every effect ($\eta$) visible to $\eta_1$
in $\E$ to be visible to $\eta_2$ as well. Thus, later operations in a
transaction witness at least the same set of effects witnessed by the
earlier operations, if not more (hence, ``monotonic'' visibility).
Atomic visibility (\C{AtomicVis}) allows an effect $\eta_2$ of $T_j$
to witness an effect $\eta_1$ of $T_i$ only if all effects of $T_i$ in
$\E$ are also visible to $\eta_2$. Atomic visibility thus prevents a
transaction from being partially visible.  However, atomic visibility
does not prevent an uncommitted transaction from being visible. This
is addressed by \C{CommitVis}, which requires the commit effect of
$T_i$ to be visible whenever any effect of $T_i$ is visible.
